draft_final_assignment

### 2022-11-30 draft_final_assingment.Rmd
Change

textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300,
                   color = c("blue", "red"))

@@

## Wordcloud comparing Democrats and Republicans

```{r, wa }
dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups =
                     corp$party) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

textplot_wordcloud(dfmatRepDem, comparison = TRUE, max_words = 300,
                   color = c("green","blue", "red"))
```

## Wordcloud congress parties 115

```{r, wa }

corp_115 <- df %>% filter(session == 115) %>% rename(text = summary) %>% corpus()
modelpart15 <- dfm(corp_115, remove = stopwords("english"),remove_numbers = TRUE, remove_punct = TRUE, groups = corp_115$party) %>%
   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

mp15 <- textplot_wordcloud(modelpart15, comparison = TRUE, max_words = 300,
                   color = c("green","blue", "red"))
mp15
```

## Wordcloud congress parties 116

```{r, wa }

mp16 <- textplot_wordcloud(modelpart16, comparison = TRUE, max_words = 300,
                   color = c("green","blue", "red"))
mp16

>>>>

textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300, color = c("green","orange","grey"))

@@
